Syntax and Semantics of Abstract Binding Trees

### 2015-11-24 paper.tex
Begin talking about sheaves & support

\newcommand\Symbols{\mathbf{I}}
\newcommand\SymSets{\mathbb{F}_\Symbols}
\newcommand\FinSets{\mathbb{F}}
\newcommand\HypCat{\mathbf{H}}

@@

@@

Let $\Symbols$ be an infinite set of symbols. Let $\SymSets$ be the category of
finite subsets of $\Symbols$ and their injective maps; then the comma
construction $\Define{\SCtx}{\Comma{\SymSets}{\Discrete{\Sorts}}}$, with
$\Discrete{\Sorts}$ the discrete category on the set $\mathcal{S}$, is the
category of contexts of symbols, whose objects are finite sets of symbols $U$
and sort-assignments
\begin{tikzcd}[cramped]
  \IMode{U}\arrow[r, "\IMode{\mathfrak{s}}"] &\IMode{\Sorts}
\end{tikzcd}, and whose morphisms are
sort-preserving renamings; we will write $\Upsilon$ for a symbol context
$(U,\mathfrak{s})$.

Then, fix a covariant presheaf of operators
$\Of{\Operators}{\SCtx\times\Discrete{\Arities}\ra\Sets}$ such that the arrows
in $\SCtx$ lift to renamings of operators' parameters. Together, $\Sorts$ and
$\Operators$ form a \emph{signature}
$\Define{\Sigma}{\Pair{\Sorts}{\Operators}}$.

>>>>

\newcommand\SymSets{\mathbb{I}}
\newcommand\FinSets{\mathbb{F}}
\newcommand\HypCat{\mathbf{H}}

@@

\newcommand\Sheaves[1]{\mathbf{Sh}(#1)}

@@

\subsection{Symbols, contexts and their sheaves}

Let $\SymSets$ be the category of finite cardinals and their injective maps;
the the comma construction
$\Define{\SCtx}{\Comma{\SymSets}{\Discrete{\Sorts}}}$, with $\Discrete{\Sorts}$
the discrete category on the set $\Sorts$, is the category of contexts of
symbols whose objects are finite sets of symbols $U$ and sort-assignments
\begin{tikzcd}[cramped]
  \IMode{U}\arrow[r, "\IMode{\mathfrak{s}}"] &\IMode{\Sorts}
\end{tikzcd}, and whose morphisms are
sort-preserving renamings; we will write $\Upsilon$ for a symbol context
$(U,\mathfrak{s})$.

Now, a covariant presheaf $X$ on $\SCtx$ is an intensional set which is subject to
renamings
\begin{tikzcd}[cramped]
  \IMode{\Upsilon}\arrow[r, hook, "\IMode{\varrho}"] & \IMode{\Upsilon'}
\end{tikzcd};
that is, each element $\Member{m}{X(\Upsilon)}$ can be mapped to a unique
element $\Member{m\varrho}{X(\Upsilon')}$.

\begin{definition}[Support]
  For a presheaf $\Of{X}{\Sets^\SCtx}$, when
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon}\arrow[r, hook, "\IMode{\varrho}"] & \IMode{\Upsilon'}
  \end{tikzcd},
  we say that $\Upsilon$ supports $\Member{m}{\Upsilon'}$ when, for all
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon'}\arrow[r, hook, "\IMode{\varrho_1}{,} \IMode{\varrho_2}"] & \IMode{\Upsilon''}
  \end{tikzcd},
  if $\IsEq{\varrho_1\circ\varrho}{\varrho_2\circ\varrho}$ then $\IsEq{m\varrho_1}{m\varrho_2}$.
\end{definition}

Intuitively, when $\Upsilon$ supports $\Member{m}{X(\Upsilon')}$, we would
expect that we can work backward to a unique $\Of{m'}{\Upsilon}$ such that
$\IsEq{m'\varrho}{m}$; whilst this is not in general the case for presheaves
$X$, it is precisely the glueing condition for covariant sheaves on $\SCtx$
under the atomic topology. The sheaf condition, then, ensures that the notion
of support is well-behaved.

\begin{remark}
  The presentation we have given above is related both to the Schanuel topos
  and, equivalently, Pitts' category of nominal sets; we differ only in
  discussing sheaves on the category of symbol contexts $\SCtx$, as opposed to
  sheaves on finite sets of symbols $\SymSets$ (i.e.\ unisorted contexts).
\end{remark}

\subsection{Operators and signatures}

Fix a sheaf of operators
$\Of{\Operators}{\Sheaves{\OpCat{\SCtx}\times\Discrete{\Arities}}}$ such that the arrows
in $\SCtx$ lift to renamings of operators' parameters. Together, $\Sorts$ and
$\Operators$ form a \emph{signature}
$\Define{\Sigma}{\Pair{\Sorts}{\Operators}}$.
